Simulations of Ballot Polling Risk-Limiting Audits

### 2023-02-19 providence/sections/workload.tex
errorbars for real time plot
misleading plot back to just virginia
fig 12 caption

\begin{figure}
\includegraphics[width=.5\textwidth]{real_time.png}
\caption{The real time as estimated by Equation~\ref{eq:real_time} for varying $p$ with expected values as estimated by our simulations.}
\label{fig:real_time}
\end{figure}

@@

\begin{figure}
%\includegraphics[width=.5\textwidth]{misleading_limits.png}
\includegraphics[width=.5\textwidth]{combined_misleading.png}
\caption{The proportion of simulated \Providence audits for the Virginia and pilot contest parameters that had a \emph{misleading sample} in any round.}
\label{fig:misleading}
\end{figure}

>>>>

\begin{figure}
%\includegraphics[width=.5\textwidth]{real_time.png}
\includegraphics[width=.5\textwidth]{real_time_errorbars.png}
\caption{The real time as estimated by Equation~\ref{eq:real_time} for varying $p$ with expected values as estimated by our simulations. Error bars show the $0.25$ and $0.75$ quantiles. Unlike Figures \ref{fig:avg_bals}, \ref{fig:avg_bals_ratio}, and \ref{fig:with_round_workload}, the quantiles stil differ for large $p$ because the first round size is no longer a constant; the number of ballots drawn in the first round in Fairfax County is variable.}
\label{fig:real_time}
\end{figure}

@@

\begin{figure}
\includegraphics[width=.5\textwidth]{misleading_limits.png}
%\includegraphics[width=.5\textwidth]{combined_misleading.png}
\caption{The proportion of simulated \Providence audits for the Virginia and pilot contest parameters that had a \emph{misleading sample} in any round.}
\label{fig:misleading}
\end{figure}
